\phantomsection
\begin{thebibliography}{}
	\bibitem{Diffgeo_Intro}
	J.M. Lee. \textbf{Introduction to Smooth Manifolds}, Graduate Texts in Mathematics 218, Springer, second edition, 2012\label{Diffgeo_Intro}

  \bibitem{Diffgeo_Merry}
	Will J. Merry. \textbf{Lecture Notes on Differential Geometry}, \url{https://www.merry.io/courses/differential-geometry/}, HS2020/FS2021\label{Diffgeo_Merry}

  \bibitem{Costello}
  K. Costello. \textbf{Renormalization and Effective Field Theory}, \url{https://web.archive.org/web/20160304134950/http://math.northwestern.edu/~costello/renormalization_book.pdf}, Mathematical Surveys and Monographs, Volume 170, American Mathematical Society\label{Costello}

  \bibitem{QFStrings}
  Deligne, Etingof, Freed, Jeffrey, Kazhdan, Morgan, Morrison, Witten. \textbf{Quantum Fields and Strings: A Course for Mathematicians}, American Mathematical Society, Institute for Advanced Study. Not the book but all main material: \url{https://www.ias.edu/math/qft}\label{QFStrings}

  \bibitem{IntroSusy}
  A.S. Cattaneo, F. Schaetz. \textbf{Introduction to Supergeometry}, \url{https://arxiv.org/abs/1011.3401v2}\label{IntroSusy}

  \bibitem{AlgebraicGeometry}
  R. Hartshorne. \textbf{Algebraic Geometry}, \url{https://link.springer.com/book/10.1007/978-1-4757-3849-0}, mainly chapter $2.1$\label{AlgebraicGeometry}

  \bibitem{ModernDiffgeo}
  C. J. Isham. \textbf{Modern differential geometry for physicists}, \url{https://cdn.preterhuman.net/texts/science_and_technology/physics/Mathematical_Physics/Modern%20Differential%20Geometry%20for%20Physicists%202nd%20ed.,%20-%20C.%20Isham.pdf}, mainly chapters $5.2$, $5.3$, $6.1$.\label{ModernDiffgeo}

  \bibitem{AlgebraicTopology}
  A. Hatcher. \textbf{Algebraic Topology}, \url{http://pi.math.cornell.edu/~hatcher/AT/ATplain.pdf}, mainly chapter 2\label{AlgebraicTopology}


\end{thebibliography}
